%* 
%* ------------------------------------------------------------------
%* FCFTutorial.tex - Tutorial chapter for the Freight Car Forwarder (V2)
%* Created by Robert Heller on Sat Apr 21 11:17:20 2007
%* ------------------------------------------------------------------
%* Modification History: $Log$
%* Modification History: Revision 1.1  2007/05/06 12:49:40  heller
%* Modification History: Lock down  for 2.1.8 release candidate 1
%* Modification History:
%* Modification History: Revision 1.1  2002/07/28 14:03:50  heller
%* Modification History: Add it copyright notice headers
%* Modification History:
%* ------------------------------------------------------------------
%* Contents:
%* ------------------------------------------------------------------
%*  
%*     Model RR System, Version 2
%*     Copyright (C) 1994,1995,2002-2005  Robert Heller D/B/A Deepwoods Software
%* 			51 Locke Hill Road
%* 			Wendell, MA 01379-9728
%* 
%*     This program is free software; you can redistribute it and/or modify
%*     it under the terms of the GNU General Public License as published by
%*     the Free Software Foundation; either version 2 of the License, or
%*     (at your option) any later version.
%* 
%*     This program is distributed in the hope that it will be useful,
%*     but WITHOUT ANY WARRANTY; without even the implied warranty of
%*     MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%*     GNU General Public License for more details.
%* 
%*     You should have received a copy of the GNU General Public License
%*     along with this program; if not, write to the Free Software
%*     Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%* 
%*  
%* 

\chapter{Freight Car Forwarder (V2) Tutorial}
\label{chpt:fcf:Tutorial}
\typeout{$Id$}


\index{Freight Car Forwarder!Tutorial|(} The Freight Car Forwarder is a
program designed to simulate freight car traffic on your model
railroad.  It does this by matching types of freight cars with
industries.  Specific types of freight cars are meant to carry specific
types of commodities and specific industries produce or consume
specific types of commodities.

The Freight Car Forwarder program uses a collection of data files,
which describe the system layout (system file), the industries
(industry file), the train that will move the cars (trains file), and
the cars themselves (the cars file).  There are some additional files,
including an owner's file and a car types file, as well as a file for
statistics.  All of these files are plain text files--See
Section~\ref{sect:fcf:Files} and  Section~\ref{sect:fcf:File Formats}
for more information on these files and their formats.

\section{Loading System Data}

The Freight Car Forwarder starts loading data by opening and reading
the system file, using either the file menu's \verb=Open...= item or open file
button on the toolbar.  This file contains the path names of the other
files, which are assumed to be relative to the directory (folder) that
contains the system file.  All of the system data is loaded into a
large data structure, which is then used by the program to simulate car
movements. Only car data is altered by the Freight Car Forwarder and the only
files that ever get re-written are the cars and statistics files.  The
other data files are never altered by the Freight Car Forwarder.  These
file can be edited using a plain text editor, such as Notepad
(MS-Windows) or Emacs (UNIX), should this be needed, as industries or
trains are added or removed, etc.

\section{Assigning Cars}

  In order to move cars, the cars need to be \emph{assigned}, that is, they
need to have a destination set, either to be loaded (if empty) or
unloaded (if loaded).  The Car Assignment procedure performs this task.

\section{Running Trains}

Once cars has been assigned, they need to be moved.  Cars are moved on
trains, and this is done with the run trains procedures.  There are
three of these procedures: Run All Trains in Operating Session, Run
Boxmoves, and Run One Train at a time.  The run trains procedures
simulate the actual movement of cars and determines which trains will
move which cars and in what order.  From this simulation, a set of yard
and switch lists can be generated and printed out for use during your
operating session.

\section{Printing Yard Lists}

Once the trains have been run, yard and switch lists can be printed
out, using the print yard lists menu.

\section{Generating Reports}

Various reports can also be generated and printed using the reports
menu. 

\section{Other activities}

Other activities include adding, removing, and editing cars and
displaying various state information, such as assigned and unassigned
cars, car movement information, lists of trains, and lists of
industries, stations, and divisions.
\index{Freight Car Forwarder!Tutorial|)} 
