%* 
%* ------------------------------------------------------------------
%* Model Railroad System by Deepwoods Software
%* ------------------------------------------------------------------
%* Install.tex - Installing
%* Created by Robert Heller on Tue Mar  5 08:38:18 2002
%* ------------------------------------------------------------------
%* Modification History: $Log$
%* Modification History: Revision 1.1  2002/11/09 21:21:07  heller
%* Modification History: Time Table User Manual
%* Modification History:
%* ------------------------------------------------------------------
%* Contents:
%* ------------------------------------------------------------------
%*  
%*     Model RR System, Version 2
%*     Copyright (C) 1994-2002  Robert Heller D/B/A Deepwoods Software
%* 			51 Locke Hill Road
%* 			Wendell, MA 01379-9728
%* 
%*     This program is free software; you can redistribute it and/or modify
%*     it under the terms of the GNU General Public License as published by
%*     the Free Software Foundation; either version 2 of the License, or
%*     (at your option) any later version.
%* 
%*     This program is distributed in the hope that it will be useful,
%*     but WITHOUT ANY WARRANTY; without even the implied warranty of
%*     MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%*     GNU General Public License for more details.
%* 
%*     You should have received a copy of the GNU General Public License
%*     along with this program; if not, write to the Free Software
%*     Foundation, Inc., 675 Mass Ave, Cambridge, MA 02139, USA.
%* 
%*  
%* 

\chapter{Installation}
\label{chapt:Installation}

In order for this package to work you need Tcl/Tk installed on your
system.  Visit \url{http://tcl.sourceforge.net/} for information on where to
get Tcl/Tk for your system.  There are binary self-installers for
MS-Windows and MacOS, as well as source and binary distributions for
UNIX and Linux.

The code requires at least version 8.0 of Tcl/Tk.  The current stable
version of Tcl/Tk is 8.3.

Once you have downloaded and installed Tcl/Tk, you then need to put the
code files, mrrTimeTable.tcl, pkgIndex.tcl, StdMenuBar.tcl, and
MakeTimeTable.tcl along with the graphics files, DeepwoodsBanner.gif and
banner.gif, in a common directory.  Under UNIX and Linux, check the
first line mrrTimeTable.tcl and make sure you have the correct path to
your wish executable and make sure mrrTimeTable.tcl has its executable
mode bit set ({\tt chmod +x mrrTimeTable.tcl}).  Under MS-Windows, you should
already have .tcl files bound to wish, so you should already be set. 
For MacOS visit \url{http://dev.scriptics.com/software/mac/} for detailed
information.

In order to be able to create hard copy time tables, you need to
install \LaTeX.  Visit \url{http://www.tug.org/} and select the {\tt
Interesting URLs} link to find free, shareware, and commercial
distributions of \LaTeX\ for UNIX/Linux, MS-Windows, and MacOS.

If you don't have dvidvi installed on your system it is included with
this package.  You should edit the Makefile and then type {\tt make dvidvi}.
Dvidvi is useful for printing double sided documents on a single-sided
printer.  Be sure to edit MakeTimeTable.tcl to set up the paths to
various programs, if they are not on your path.  You can also set the
dvips options suitable to your preferences.





